\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-07-31 popl-2019-journal-v/proving-full-abstraction.tex
[POPLjv] Update figure

  \draw[gray, fill=gray, fill opacity=.4] (3,5) rectangle (5,0.5) node[fitting node] (w2l) { };
  \draw (w2r2) edge[->,in=0, out=210] (w2l.east);

@@

  \node[draw,rectangle, black, minimum size=2mm] (w1r) at (-2,5) {  };
  \node[fit=(w1r),black,inner sep=-\pgflinewidth,cross out, draw] (test) { };
  \draw (w1r2) edge[->, out=0] (w1r);

@@

  \node[draw,rectangle, black, minimum size=2mm] (w2r) at (6.5,5) {  };
  \node[fit=(w2r),black,inner sep=-\pgflinewidth,cross out, draw] (test) { };
  \draw (w2r2) edge[->, out=180,in=45] (w2r);

  \draw[gray, fill=gray, fill opacity=.4] (3,5) rectangle (5,0.5) node[fitting node] (w2l) { };
  \draw (w2r3) edge[->,in=0, out=210] (w2l.east);

@@

   \matrix [draw,above right, column sep=1.5mm,xshift=.4cm,yshift=.4cm] at (current bounding box.south west) {
  &\node[red, fill=red, fill opacity=.5,minimum size=0.4cm,label=right:{\footnotesize Shared region}] {}; \\
    &\node[gray, fill=gray, fill opacity=.4,minimum size=0.4cm,label=right:{\footnotesize Shadow region}] {}; \\
     \node[green, fill=green, fill opacity=.7,minimum size=0.4cm] {};
    &\node[blue, fill=blue, fill opacity=.6,minimum size=0.4cm,draw,label=right:{\footnotesize Spatial region}] {}; \\
    &\node[draw,rectangle, black, minimum size=4mm] (rev) {};
    \node[fit=(rev),black,inner sep=-\pgflinewidth,cross out, draw, label=right:{\footnotesize Revoked region}] {};\\
    \node[minimum size=0.4cm] (ln) {}; & \node[minimum size=0.4cm,label=right:{\footnotesize Normal capability}] (rn) {};\\
    \node[minimum size=0.4cm] (ll) {}; & \node[minimum size=0.4cm,label=right:{\footnotesize Linear capability}] (rl) {};\\
};
\draw (ln.west) edge[-latex,out=-20,in=160] (rn.east);
\draw (ll.west) edge[-latex,out=-20,in=160,dashed] (rl.east);

>>>>

  \draw[darkgray, fill=darkgray, fill opacity=.4] (3,5) rectangle (5,0.5) node[fitting node] (w2l) { };
  \draw (w2r2) edge[->,in=0, out=210] (w2l.east);

@@

  \node[draw,rectangle, black, minimum size=4mm] (w1r) at (-2,5) {  };
  \node[fit=(w1r),black,inner sep=-\pgflinewidth,cross out, draw] (test) { };
  \draw (w1r2) edge[->, out=0] (w1r);

@@

  \node[draw,rectangle, black, minimum size=4mm] (w2r) at (6.5,5) {  };
  \node[fit=(w2r),black,inner sep=-\pgflinewidth,cross out, draw] (test) { };
  \draw (w2r2) edge[->, out=180,in=45] (w2r);

  \draw[lightgray, fill=lightgray, fill opacity=.4] (3,5) rectangle (5,0.5) node[fitting node] (w2l) { };
  \draw (w2r3) edge[->,in=0, out=210] (w2l.east);

@@

   \matrix [draw,above right, column sep=1.5mm,xshift=.4cm,yshift=.4cm] at (current bounding box.south west) {
    &\node[red, fill=red, fill opacity=.5,minimum size=0.4cm,label=right:{\footnotesize Shared region}] {}; \\
     \node[darkgray, fill=darkgray, fill opacity=.4,minimum size=0.4cm] {};
    &\node[lightgray, fill=lightgray, fill opacity=.4,minimum size=0.4cm,label=right:{\footnotesize Shadow regions}] {}; \\
     \node[green, fill=green, fill opacity=.7,minimum size=0.4cm] {};
    &\node[blue, fill=blue, fill opacity=.6,minimum size=0.4cm,draw,label=right:{\footnotesize Spatial regions}] {}; \\
    &\node[draw,rectangle, black, minimum size=4mm] (rev) {};
     \node[fit=(rev),black,inner sep=-\pgflinewidth,cross out, draw, label=right:{\footnotesize Revoked region}] {};\\
     \node[minimum size=0.4cm] (ln) {}; & \node[minimum size=0.4cm,label=right:{\footnotesize Normal capability}] (rn) {};\\
     \node[minimum size=0.4cm] (ll) {}; & \node[minimum size=0.4cm,label=right:{\footnotesize Linear capability}] (rl) {};\\
};
\draw (ln.west) edge[-latex,out=-20,in=160] (rn.east);
\draw (ll.west) edge[-latex,out=-20,in=160,dashed] (rl.east);
